Cooperative Kernels: Safe Multitasking for Blocking Algorithms on GPUs

### 2016-11-15 write-ups/PLDI/paper.tex
Add paragraph on porting irregular GPU applications

\begin{table}
\small
\centering
\begin{tabular}{ l c c c }
app & resizing barriers & ckill - cfork & transmit vars\\
\hline
\rowcolor{Gray1}
color & 2 / 2 & 0 - 0 & 4\\
\rowcolor{Gray1}
mis & 3 / 3 & 0 - 0 & 0\\
\rowcolor{Gray1}
bc & 3 / 6 & 0 - 0 & 3\\
\rowcolor{Gray1}
p-sssp & 3 / 3 & 0 - 0 & 0 \\
\rowcolor{Gray2}
bfs & 2 / 2 & 0 - 0  & 4 \\
\rowcolor{Gray2}
l-sssp & 2 / 2 & 0 - 0  & 4 \\
\rowcolor{Gray3}
octree & 0 / 0 & 1 - 1 & 0\\
\rowcolor{Gray3}
game & 0 / 0 & 1 - 1 & 0\\
\end{tabular} \\
\vspace{.2cm}
\crule[Gray1]{.2cm}{.2cm} - Pannotia \hspace{.4cm} \crule[Gray2]{.2cm}{.2cm} - Lonestar GPU  \hspace{.4cm}  \crule[Gray3]{.2cm}{.2cm} - work stealing
\caption{Blocking GPU applications investigated}
\label{tab:applications}
\end{table}

@@

\HEComment{This is more or less already done in section
\ref{sec:programmingguidelines} , maybe no need to rewrite here?}

\ADComment{Give stats on how many variables had to be marked with
  $\transmit$ (i.e., occurred in the restoration context), how many
  barriers we changed to resizing, how many offer kill and offer fork
  calls we included.}  \TSComment{check out
  Table~\ref{tab:applications}. The barrier column shows how many of
  the original barriers were ported to resizing barriers. In all cases
  except bc we converted all of them. The only reason why bc is
  different is because barriers occur deeper in the call stack and our
  prototype cannot handle that. The algorithm itself is compatable
  (i.e. changing these barriers is as easy as any other, there is
  nothing special about them.)}

>>>>

\begin{table}
\small
\centering
\begin{tabular}{ l c c c }
App. & resizing barriers & kill - fork & transmit vars\\
\hline
\rowcolor{Gray1}
color & 2 / 2 & 0 - 0 & 4\\
\rowcolor{Gray1}
mis & 3 / 3 & 0 - 0 & 0\\
\rowcolor{Gray1}
bc & 3 / 6 & 0 - 0 & 3\\
\rowcolor{Gray1}
p-sssp & 3 / 3 & 0 - 0 & 0 \\
\rowcolor{Gray2}
bfs & 2 / 2 & 0 - 0  & 4 \\
\rowcolor{Gray2}
l-sssp & 2 / 2 & 0 - 0  & 4 \\
\rowcolor{Gray3}
octree & 0 / 0 & 1 - 1 & 0\\
\rowcolor{Gray3}
game & 0 / 0 & 1 - 1 & 0\\
\end{tabular} \\
\vspace{.2cm}
\crule[Gray1]{.2cm}{.2cm} - Pannotia \hspace{.4cm} \crule[Gray2]{.2cm}{.2cm} - Lonestar GPU  \hspace{.4cm}  \crule[Gray3]{.2cm}{.2cm} - work stealing
\caption{Blocking GPU applications investigated}
\label{tab:applications}
\end{table}

\HEComment{Add citations for pannotia, lonestar, workstealing}

\mytablong~\ref{tab:applications} gives an overview of the 8 irregular
algorithms that we ported to cooperative kernels. Among them, 6 are
graph algorithms, based on Pannotia and Lonestar GPU application suite,
using global barriers; we indicate how many barriers become resizing
ones out of the total number of barriers, and how many variables need to
be transmitted. In all cases all barriers were converted, except for bc
which contains barriers deeper in the call stack, a case not supported
by our prototype. Still, these barriers could in principle also be
converted.  The remaining 2 algorithms are workstealing applications:
each required the addition of $\offerfork$ and $\offerkill$ at the start
of the main loop, and no variables needed to be transmitted. For all
these examples the porting to cooperative kernels was pretty
straightforward and did not require to bend the original algorithm.

@@

\ADComment{Give stats on how many variables had to be marked with
  $\transmit$ (i.e., occurred in the restoration context), how many
  barriers we changed to resizing, how many offer kill and offer fork
  calls we included.}

  \TSComment{check out Table~\ref{tab:applications}. The barrier column
  shows how many of the original barriers were ported to resizing
  barriers. In all cases except bc we converted all of them. The only
  reason why bc is different is because barriers occur deeper in the
  call stack and our prototype cannot handle that. The algorithm itself
  is compatable (i.e. changing these barriers is as easy as any other,
  there is nothing special about them.)}
